---
title: "Pricing Strategy Airbnb based on Negative Reviews"
author: "Rashel Mol, Noa Beekmans, Astrid Raaijmakers, Pien Korteweg, Amber Vermeer"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, echo = FALSE}
library(readr)
library(kableExtra)
library(modelsummary)
```

# Introduction 
Firsly, we cleaned the raw dataset. The descriptions of the variables are mentioned below. Based on this cleaned dataset, we executed a text analysis. The results of this analysis are shown in a sentiment plot. Furthermore, we did a topic analysis to check what topics are spoken of the most. These results are shown in the sentiment topic plot below. To conclude, we performed a regression analysis. The results are shown in model summary. Also, we briefly describe the results in the section below. To conclude, we visually checked the correlation between price and sentiment (compound).

Note: our results are based on a prototype sample. The results can differ when conducting it on the whole dataset. 

## Variable Descriptions 
The cleaned dataset "gen/temp/airbnb.csv", consists of the following variables. 

#### ID 
ID is a numeric variable. Every listing has an unique ID. 

#### Name 
Name is a character variable. Name of the listing. 

#### Neighbourhood
Neighbourhood is a factor variable. The neighbourhood in which the listing is located. There are 22 classified neighbourhoods. 

#### Room Type
Room type is a factor variable. There are 4 possible room types.

#### Accommodates
Accomodates is a numeric variable. Accommodates is the number of guests that can stay in the listing.

#### Comments
Comments is a character variable. Comments are the reviews about the listing. 

#### Year
Year is a numeric variable. Year is the year the review is written.

#### Price
Price is a numeric variable. Price is the price in dollars per night. 

```{r, echo = FALSE}
airbnb <- read_csv("../gen/temp/airbnb.csv")
summary(airbnb)
```

## Sentiment Analysis

```{r, echo = FALSE, fig.align='center', out.height='40%'}
knitr::include_graphics('../gen/output/plot_sentiment.pdf')
```

Based on the plot above, which is generated in the text_analysis.R script, we can see the following:
- The vast majority of reviews in the Airbnb dataset is defined positive.
- Only a very small part of the reviews in this same dataset is considered negative.

Therefore, we can conclude that the majority of reviews created by Airbnb guests has a positive nature.

## Topic Analysis

```{r, echo = FALSE, fig.align='center', out.height='40%'}
knitr::include_graphics('../gen/output/sentiment_topics.pdf')
```
Noticeable is that most reviews are about Location and Amenity. A relatively small number is about Activity and Host. 

The plot above shows the topics most often mentioned in the reviews written by Airbnb guests. Remarkable is that most reviews are about Location and Amenity. A relatively small number is about Activity and Host.

## Regression Analysis

### Model Summary 

```{r, echo = FALSE}
sample_airbnb <- read_csv("../gen/temp/sample_airbnb.csv")
regr <- lm(compound ~ price, data = sample_airbnb)
msummary(regr)
```
The effect of price on compound (sentiment) is non significant, with a p-value of .372. There is very little variation explained by the model, resulting in a R square of .002. 

### Plot Price and Compound 

```{r, echo = FALSE, fig.align='center', out.height='40%'}
knitr::include_graphics('../gen/output/plot_regression.pdf')
```
As we expected based on the regression results, there is visually no correlation to be seen between price and compound (sentiment). Also, as earlier mentioned in one of the intermediate plots, most reviews are labeled as positive. 

However, since only a limited sample size has been used in this analysis, one should be careful about rejecting this hypothesis. A significant relationship could still be identified when analyzing the full dataset.